temp

### 2024-10-10 paper/paper.qmd

---
title: "MarriageLicense"
subtitle: "My subtitle if needed"
author: 
  - Mariko Lee
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "temp"
subtitle: "My subtitle if needed"
author: 
  - Mariko Lee
  - Karen Riani
  - Cristina Su Lam
thanks: "Code and data are available at: https://projects.fivethirtyeight.com/polls/president-general/2024/national/"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---
